A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2022-05-16 review/response.Rmd

---
title: "Response to review"
author: "Stephanie Kobakian and Dianne Cook"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Thank you for the review of our article. These are the changes that we have made in response. The review comment is indented italic, and our response follows in regular text.

First, we have reformatted the paper to use the `rjtools` package.

We have made a simpler code example that will run from start to end of the algorithm, but also kept the full Australia example created from data provided with the source files of the article.

> *The article is clearly written and does a good job of discussing previous mapping approaches as well as their limitations. The figures were useful in this regard, as they make the textual discussion in the background sections easily understandable even for users less experienced in geography. The flowchart summarizing the algorithm was also useful. I would suggest some minor substantive revisions to improve the substance of the background as well as the clarity of the package’s functionality. First, the discussion of the pros and cons of choropleth maps and various forms of cartograms was good, but I would like more information about the value of hexagons over other shapes. Why not circles or squares or triangles? Hexagons do have advantages, but adding a few more sentences about this would be useful, especially for non-specialist users. Second, other R packages for mapping can be cited, including cartogram (Jeworutzki et al 2020) and tilemaps (McNeill and Hale 2017). Third, I might recommend putting the “implementation” section above the “user choices” section. Fourth, and this is probably a personal preference, the implementation section could be improved by adding a simple table listing the main functions in the package and a brief summary of what they do. This makes the information more easily accessible to the reader. Fifth, the implementation section provides a running example, but please include some sample code directly in the article. This makes the package more accessible to users. It is not necessary to include all code of course, but some of the more important functions that produce a core visualization should be provided directly in the text.*

> *There were also a few minor typos that should be fixed (e.g., “tyroid” in the caption of Figure 3 and the comma beginning the third line of the second paragraph of the “implementation” section). The last two sentences of the first paragraph of the discussion section are also identical to the next two sentences. Overall, these revisions to the article are relatively minor and manageable.*

> *The package itself seems to be reasonably well-organized, the code is clean, and there is sufficient built-in documentation. The progress bars are also useful. I don’t have any major suggestions for improving the functionality of the package itself, other than the fact that I couldn’t reproduce the example maps in the implementation section because the data were not self-contained. The article says that the example is reproducible using data from the absmapsdata package, but in the provided RMD file the object “fort_aus” can be traced back to the “SIR Downloadable Data.csv” dataset, which is from an external source (and also not available on the github repo). Forgive me if I am missing something here (and it is possible that I am). If not, these SIR data should be embedded or example code fixed to not be dependent on the SIR data so that the illustrative maps are reproducible.*

### 2022-05-16 kobakian-cook.Rmd
gganimate as CRAN pkg
reviews and start on response

## Create centroids set
centroids <- sa2 %>% 
  create_centroids(., "sa2_name_2011")
## Create hexagon grid
grid <- create_grid(centroids = centroids,
                    hex_size = 0.2,
                    buffer_dist = 5)
## Allocate polygon centroids to hexagon grid points
aus_hexmap <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "sa2_name_2011",
  ## same column used in create_centroids
  hex_size = 0.2,
  ## same size used in create_grid
  hex_filter = 10,
  focal_points = capital_cities,
  width = 35,
  verbose = FALSE
)
save(aus_hexmap, file = "data/aus_hexmap.rda") }

@@

```{r contcart}
# Projected data 
sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112) %>% 
  filter(state_name_2011 == "Tasmania")
sa2thyroid_ERP <- sa2thyroid_ERP %>% 
  mutate(sva = sqrt(as.numeric(Population)/as.numeric(albers_sqkm)))

@@

tas_ggcont <- ggplot(cont) + 
  geom_sf(fill = "#D3D3D3", colour = "white", data = sa2thyroid_ERP) +
  geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
  scale_fill_identity() + guides(fill=FALSE) +
  theme_map() + ggtitle("a")
#tas_ggcont
```

```{r ncontcart}
# Non - Contiguous Cartograms
if (!file.exists("data/ncont.rda")) {
ncont <- cartogram_ncont(sa2thyroid_ERP, k = 1.5,
                         weight = "Population") %>% 
                          st_as_sf()
save(ncont, file = "data/ncont.rda")}

@@

tas_ggncont <- ggplot(ncont %>% filter(state_name_2011 == "Tasmania")) + 
  geom_sf(fill = "#D3D3D3", colour = "white",  data = sa2thyroid_ERP) +
  geom_sf(aes(fill = SIR), colour = NA) + 
  scale_fill_identity() + 
  guides(fill=FALSE) +
  theme_map() + ggtitle("b")
#tas_ggncont
```

```{r dorl}
# Non - Contiguous Dorling Cartograms
dorl <- sa2thyroid_ERP %>% 
  filter(!is.na(Population)) %>% 
  #mutate(pop = (Population/max(Population))*10) %>% # helpful for all of Australia
  cartogram_dorling(., weight = "Population", k = 0.2, m_weight = 1) %>% st_as_sf()
d <- st_bbox(dorl)
tas_ggdorl <- ggplot(dorl) +
  geom_sf(fill = "#D3D3D3", colour = "white",  data = sa2thyroid_ERP) + 
  geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
  scale_fill_identity() +
  guides(fill = FALSE) +
  theme_map() + ggtitle("c")
#tas_ggdorl
```

@@

Creating an animation connecting these two displays can allow users to grasp the meaning of the connected hexagons. It will also highlight the density of the communities using the rapid expansion of the inner-city areas, these hexagons will move the furthest and will move rapidly in the animation from their geographic locations. The rapid decrease in size of the large rural areas can show the large size of their collective landmass. The \pkg{gganimate} [@gganimate] package can be used to make an animation. It connects the polygons for each area in the two displays using the \code{sf\_id} variable, the names of the statistical areas, and creates intermediate displays as they geographic areas shrink or expand to the chosen hexagon size.

>>>>

## Create centroids set
centroids <- sa2 %>% 
  create_centroids(., "sa2_name_2011")
## Create hexagon grid
grid <- create_grid(centroids = centroids,
                    hex_size = 0.1,
                    buffer_dist = 5)
## Allocate polygon centroids to hexagon grid points
aus_hexmap <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "sa2_name_2011",
  ## same column used in create_centroids
  hex_size = 0.2,
  ## same size used in create_grid
  hex_filter = 10,
  focal_points = capital_cities,
  width = 35,
  verbose = FALSE
)
save(aus_hexmap, file = "data/aus_hexmap.rda") 
}

@@

```{r contcart}
# Projected data 
sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112) %>% 
  filter(state_name_2011 == "Tasmania")
sa2thyroid_ERP <- sa2thyroid_ERP %>% 
  #mutate(sva = sqrt(as.numeric(Population)/as.numeric(albers_sqkm)))
  mutate(sva = sqrt(as.numeric(Population)/as.numeric(areasqkm_2011)))

@@

tas_ggcont <- ggplot(cont) + 
  geom_sf(fill = "#D3D3D3", colour = "white", data = sa2thyroid_ERP) +
  geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
  scale_fill_identity() + guides(fill = "none") +
  theme_map() + ggtitle("a")
#tas_ggcont
```

```{r ncontcart}
# Non - Contiguous Cartograms
if (!file.exists("data/ncont.rda")) {
  ncont <- cartogram_ncont(sa2thyroid_ERP, k = 1.5,
                         weight = "Population") %>% 
                          st_as_sf()
  save(ncont, file = "data/ncont.rda")
}

@@

tas_ggncont <- ggplot(ncont %>% filter(state_name_2011 == "Tasmania")) + 
  geom_sf(fill = "#D3D3D3", colour = "white",  data = sa2thyroid_ERP) +
  geom_sf(aes(fill = SIR), colour = NA) + 
  scale_fill_identity() + 
  guides(fill = "none") +
  theme_map() + ggtitle("b")
#tas_ggncont
```

```{r dorl}
# Non - Contiguous Dorling Cartograms
dorl <- sa2thyroid_ERP %>% 
  filter(!is.na(Population)) %>% 
  #mutate(pop = (Population/max(Population))*10) %>% # helpful for all of Australia
  cartogram_dorling(., weight = "Population", k = 0.2, m_weight = 1) %>% st_as_sf()
d <- st_bbox(dorl)
tas_ggdorl <- ggplot(dorl) +
  geom_sf(fill = "#D3D3D3", colour = "white",  data = sa2thyroid_ERP) + 
  geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
  scale_fill_identity() +
  guides(fill = "none") +
  theme_map() + ggtitle("c")
#tas_ggdorl
```

@@

Creating an animation connecting these two displays can allow users to grasp the meaning of the connected hexagons. It will also highlight the density of the communities using the rapid expansion of the inner-city areas, these hexagons will move the furthest and will move rapidly in the animation from their geographic locations. The rapid decrease in size of the large rural areas can show the large size of their collective landmass. The \CRANpkg{gganimate} [@gganimate] package can be used to make an animation. It connects the polygons for each area in the two displays using the \code{sf\_id} variable, the names of the statistical areas, and creates intermediate displays as they geographic areas shrink or expand to the chosen hexagon size.

### 2022-05-16 kobakian-cook.tex
gganimate as CRAN pkg
reviews and start on response

Creating an animation connecting these two displays can allow users to
grasp the meaning of the connected hexagons. It will also highlight the
density of the communities using the rapid expansion of the inner-city
areas, these hexagons will move the furthest and will move rapidly in
the animation from their geographic locations. The rapid decrease in
size of the large rural areas can show the large size of their
collective landmass. The \pkg{gganimate} \citep{gganimate} package can
be used to make an animation. It connects the polygons for each area in
the two displays using the \code{sf\_id} variable, the names of the
statistical areas, and creates intermediate displays as they geographic
areas shrink or expand to the chosen hexagon size.

@@

\address{%
Stephanie Kobakian\\
Monash University\\%
Department of Econometrics and Business Statistics\\
%
%
%
\\\href{mailto:stephanie.kobakian@monash.edu}{\nolinkurl{stephanie.kobakian@monash.edu}}
}

\address{%
Dianne Cook\\
Monash University\\%
Department of Econometrics and Business Statistics\\
%
%
%
\\\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}
}

\address{%
Earl Duncan\\
Queensland University of Technology\\%
School of Mathematical Sciences\\
%
%
%
\\\href{mailto:earl.duncan@qut.edu.au}{\nolinkurl{earl.duncan@qut.edu.au}}
}

>>>>

Creating an animation connecting these two displays can allow users to
grasp the meaning of the connected hexagons. It will also highlight the
density of the communities using the rapid expansion of the inner-city
areas, these hexagons will move the furthest and will move rapidly in
the animation from their geographic locations. The rapid decrease in
size of the large rural areas can show the large size of their
collective landmass. The \CRANpkg{gganimate} \citep{gganimate} package
can be used to make an animation. It connects the polygons for each area
in the two displays using the \code{sf\_id} variable, the names of the
statistical areas, and creates intermediate displays as they geographic
areas shrink or expand to the chosen hexagon size.

@@

\address{%
Stephanie Kobakian\\
Monash University\\%
Department of Econometrics and Business Statistics\\
%
%
%
\href{mailto:stephanie.kobakian@monash.edu}{\nolinkurl{stephanie.kobakian@monash.edu}}%
}

\address{%
Dianne Cook\\
Monash University\\%
Department of Econometrics and Business Statistics\\
%
%
%
\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}%
}

\address{%
Earl Duncan\\
Queensland University of Technology\\%
School of Mathematical Sciences\\
%
%
%
\href{mailto:earl.duncan@qut.edu.au}{\nolinkurl{earl.duncan@qut.edu.au}}%
}
